From textual to structured Web API Descriptions\\ \large Knowledge Discovery and Data Mining Seminar 2017

### 2017-08-29 Paper/Paper_KDD.tex
small Changes

\section{Introduction}
\IEEEPARstart{A}{pplication} Programming Interfaces (API) are not just a way to give developers access to software or services anymore. A whole business economy has established around the concept of exposing APIs in order to provide access and services. Programmable Web currently lists 15839 public available API (State June 2017). While ProgrammableWeb represent as set of manually collected APIs, APIHound claims to have crawled and indexed over 50000 APIs.
According to 3scale CEO Steve Willmott, eBay, Flickr, and Salesforce were among the companies that helped popularize the API [1] leading towards entire business models evolving around API services and strategies. Along came new terminologies to define this industry such as API Economy and Business to Developer (B2D).

API Economy is defined as the positive affect APIs can have on an organization’s profitability. [2]
It can be loosely compared to the prestige of patents plaques. The more holistic a company provides APIs the more developers can make use of it. Well documented API’s attracts developers to either actively consume APIs or even build their own business on top of it.

\begin{figure}[!t]
\centering
\includegraphics[width= 3in]{img/APIcycle.png}
\caption{MuleSoft on API Econom}
\label{fig_sim}
\end{figure}

@@

\subsection{Linked Web API Dataset}
Starting point was the Linked Web API dataset [1] with 9.850 APIs. Besides short descriptions of the API, it inherits also semantic annotations and links between different attributes like title, tags and links to websites. For our purpose only the descriptions were relevant. The first inspection shows, that the descriptions were too short. Since we want to cluster the APIs on similarity based on their descriptions, those were crucial. First solution was to crawl the website of the API. This seemed to be easily done, since the dataset also had a link to the API documentation website. When checking the links, we found out that 78 \% (Fig. 1) of the links were missing. The remaining 1.500 links where leading to any subpages, but not to the actual API documentation. Therefore, crawling those sites would result in a poor data quality, since we have no control over which textual content would be crawled.

@@

\subsection{Precision and Recall}
The other idea of fixing the runtime problem was using precision and recall as coefficient for similarity. These two are also often used for cluster similarity measurement. Basically, the use the same concept with classifying if one api is true positive, false positive, true negative or false negative sorted into a clustered according to a certain set of clusters that is assumed to be correct. The advantage is that we do not need to build pairs for calculation and can decrease runtime by that.

@@

>>>>

\section{Introduction}
\IEEEPARstart{A}{pplication} Programming Interfaces (API) are not just a way to give developers access to software or services anymore. A whole business economy has established around the concept of exposing APIs in order to provide access and services. Programmable Web currently lists 15839 public available API (State June 2017). While ProgrammableWeb represent as set of manually collected APIs, APIHound claims to have crawled and indexed over 50000 APIs.
According to 3scale CEO Steve Willmott, eBay, Flickr, and Salesforce were among the companies that helped popularize the API \cite{tmcnet} leading towards entire business models evolving around API services and strategies. Along came new terminologies to define this industry such as API Economy and Business to Developer (B2D).

API Economy is defined as the positive affect APIs can have on an organization’s profitability.\cite{mulesoft}
It can be loosely compared to the prestige of patents plaques. The more holistic a company provides APIs the more developers can make use of it. Well documented API’s attracts developers to either actively consume APIs or even build their own business on top of it.

\begin{figure}[!t]
\centering
\includegraphics[width= 3in]{img/APIcycle.png}
\caption{MuleSoft on API Econom \cite{mulesoft}}
\label{fig_sim}
\end{figure}

@@

\subsection{Linked Web API Dataset}
Starting point was the Linked Web API dataset \cite{dojchinovskilinked} with 9.850 APIs. Besides short descriptions of the API, it inherits also semantic annotations and links between different attributes like title, tags and links to websites. For our purpose only the descriptions were relevant. The first inspection shows, that the descriptions were too short. Since we want to cluster the APIs on similarity based on their descriptions, those were crucial. First solution was to crawl the website of the API. This seemed to be easily done, since the dataset also had a link to the API documentation website. When checking the links, we found out that 78 \% (Fig. 1) of the links were missing. The remaining 1.500 links where leading to any subpages, but not to the actual API documentation. Therefore, crawling those sites would result in a poor data quality, since we have no control over which textual content would be crawled.

@@

\subsection{Precision and Recall}
The other idea of fixing the runtime problem was using precision and recall as coefficient for similarity. These two are also often used for cluster similarity measurement. Basically, the use the same concept with classifying if one api is true positive, false positive, true negative or false negative sorted into a clustered according to a certain set of clusters that is assumed to be correct. The advantage is that we do not need to build pairs for calculation and can decrease runtime by that. \cite{powers2011evaluation}

@@

\section{Conclusion}
